---
title: "`r paste0('Country note: ', params$iso3)`"
author: "Centre for Entrepreneurship, SMEs, Regions and Cities"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
params:
  iso3: "KOR"  # options: "KOR", "MEX", "GBR"
  show_code: false
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = params$show_code, message = FALSE)
```

```{r libraries}
library(tidyverse)
library(countrycode)
library(here)
```

```{r theme}
oecd_theme <- function() {
  theme(
    axis.title = element_blank(),
    axis.text.x = element_text(size = 10, colour = "black", angle = 45, hjust = 1),
    axis.text.y = element_text(size = 10, colour = "black"),
    axis.line = element_line(colour = "black"),
    axis.ticks = element_line(color = "black"),
    axis.ticks.length = unit(-0.15, "cm"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "#E9E9E9"),
    legend.text = element_text(size = 10),
    legend.title = element_blank(),
    legend.key = element_rect(color = "#E9E9E9", fill = "#E9E9E9"),
    legend.background = element_rect(fill = "#E9E9E9"),
    legend.box.background = element_rect(color = "#E9E9E9", fill = "#E9E9E9"),
    legend.box.margin = margin(0, 0.5, 0, 0.5, "cm"),
    legend.key.size = unit(0.7, "line"),
    legend.position = "top",
    legend.direction = "horizontal",
    legend.box = "horizontal"
  )
}
```

```{r country-name}
country <- countrycode(params$iso3, "iso3c", "country.name")
```


## Labour productivity in `r country`

```{r data-prep}
dir_data <- here("data")
data_raw <- read_rds(fs::path(dir_data, "worker_productivity.rds")) %>% 
  mutate(iso3 = fct_reorder(iso3, -max)) %>%
  pivot_longer(
    c(average, min, max),
    names_to = "category",
    values_to = "value"
  ) %>%
  mutate(
    value = value / 1000,
    category = factor(
      category,
      levels = c("min", "average", "max"),
      labels = c("Minimum region", "National average", "Maximum region")
    ))
data_figure <- data_raw %>%
  filter(iso3 %in% c("IRL", params$iso3, "BGR"))
```

```{r value} 
average_gva <- data_figure %>% 
  filter(iso3 == params$iso3, category == "National average") %>% 
  pull(value)
max_gva <- data_figure %>% 
  filter(iso3 == params$iso3, category == "Maximum region") %>% 
  pull(value)
min_gva <- data_figure %>% 
  filter(iso3 == params$iso3, category == "Minimum region") %>% 
  pull(value)
```

On average, labour productivity in `r country` is `r scales::comma(average_gva * 1000)` USD per worker. The region with the highest labour productivity has a gross value added per worker of `r scales::comma(max_gva * 1000)` USD. Its GVA per worker is `r round(max_gva / min_gva, digits = 1)` times that of the region with the lowest GVA per worker at `r scales::comma(min_gva * 1000)` USD. 

```{r fig, fig.width=6, fig.height=4.5}
data_figure %>%
  ggplot(aes(x = iso3, y = value)) +
  geom_line(colour = "#00A9CB", size = 3) +
  geom_point(aes(colour = category, shape = category), size = 3) +
  geom_point(
    data = filter(data_figure, category == "National average"),
    colour = "black", size = 3, shape = 18
  ) +
  geom_hline(
    aes(yintercept = 57.74, linetype = "OECD average"),
    colour = "#1461B3"
    ) +
  labs(subtitle = "'000 USD per worker") +
  scale_colour_manual(values = c("white", "black", "#0060B3")) +
  scale_shape_manual(values = c(16, 18, 16)) +
  scale_y_continuous(
    limits = c(0, 220), expand = c(0, 0),
    breaks = seq(0, 220, by = 20)
  ) +
  oecd_theme()
```

This is an example of country note to the [Regions and Cities at a Glance report](https://www.oecd.org/cfe/oecd-regions-and-cities-at-a-glance-26173212.htm). More data is available at <https://regions-cities-atlas.oecd.org/>.