---
title: "R programming basics"
author: "María Paula Caldas"
ta: "Jolien Noels"
date: "2021-09-30"
description: ""
params:
  module: "3"
  url_slides:  "https://mpaulacaldas.github.io/cfe-r-training/03_programming.html"
  url_project: "https://rstudio.cloud/project/2940340"
  url_teams: "https://teams.microsoft.com/l/team/19%3aewi8FvNssJHrCsxFDSJbA7IL4q4kGH0E8IRMfMp8zPA1%40thread.tacv2/conversations?groupId=c957fd70-0f85-4bcc-b3a4-e453919316de&tenantId=ac41c7d4-1f61-460d-b0f4-fc925a2b471c"
  url_github: "https://github.com/mpaulacaldas/cfe-r-training"
  png_background: "img/gradient-background.png"
  png_break: "https://images.unsplash.com/photo-1421986872218-300a0fea5895?ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&ixlib=rb-1.2.1&auto=format&fit=crop&w=634&q=80"
output:
  xaringan::moon_reader:
    css: ["default", "cfe-fonts.css", "cfe.css"]
    lib_dir: libs
    seal: false # to customise the title slide
    nature:
      highlightStyle: github
      highlightLines: true
      highlightLanguage: ["r", "css", "yaml"]
      countIncrementalSlides: true
      ratio: "16:9"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.retina = 3, # https://community.rstudio.com/t/size-of-image-in-xaringan-slides/21319/12
  collapse = TRUE,
  comment = "#>"
  )

xaringanExtra::use_xaringan_extra(c(
  "tile_view",  # type 'o' to see an overview of the slides
  "clipboard",  # copy-paste of the code chunks
  "panelset",   # panels, https://pkg.garrickadenbuie.com/xaringanExtra/panelset/
  "freezeframe" # so gifs play when we get to the slide
  ))

emoji <- function(x) paste0(emo::ji(x), "&nbsp;")
```

class: title-slide, inverse, bottom
background-image: url(`r params$png_background`)
background-size: cover

# `r rmarkdown::metadata$title`
### `r paste0("CFE R Training - Module ", params$module)`

<br/>

`r rmarkdown::metadata$author` and `r rmarkdown::metadata$ta`

---
class: middle

# Useful links

[Slides](`r params$url_slides`), if you want to navigate on your own

[RStudio Project](`r params$url_project`), to try out the exercises

[Teams Space](`r params$url_teams`), for discussions

[Github repository](`r params$url_github`), for later reference

---
class: middle

# Housekeeping matters

`r emoji("woman_raising_hand")` During the session, ask questions in the chat 
or raise your hand

`r emoji("camera")` Sessions are recorded. Remember to turn off your camera if 
its your preference

`r emoji("speech_balloon")` After the session, post follow-up questions, 
comments or reactions in the [Teams space](`r params$url_teams`)

`r emoji("pencil")` If you are going through these slides on your own, type `p` 
to see the presenter notes

???

The presenter notes are where you might also find OECD or CFE specific 
information.

---
# A regular slide

With text. Let's see the text.

```{r}
1 + 1
2 + 2 #<<
```


---
class:inverse, bottom, left

# Section division

---
# Another simple slide

With text. Let's see the text.

```{r}
summary(iris)
```

---
class: exercise

# `r emoji("pencil")` Exercise with timer

Prompt.

- Items
- Items

```{r, echo = FALSE}
countdown::countdown(minutes = 0, seconds = 2, top = 0)
```

---
class: inverse, bottom, left
background-image: url(`r params$png_break`)
background-size: cover

# Break

```{r, echo = FALSE}
countdown::countdown(minutes = 10, top = 0)
```

---
class: inverse, bottom, left
background-image: url(`r params$png_background`)
background-size: cover

# Annex

