---
title: "Our titles are not as long"
author: "María Paula Caldas"
ta: "Jolien Noels"
date: "2021-09-13"
description: ""
params:
  module: "1"
  url_slides:  ""
  url_project: ""
  url_teams: ""
  url_github: ""
  png_background: "img/gradient-background.png"
output:
  xaringan::moon_reader:
    css: ["default", "cfe-fonts.css", "cfe.css"]
    lib_dir: libs
    seal: false # to customise the title slide
    nature:
      highlightStyle: github
      highlightLines: true
      highlightLanguage: ["r", "css", "yaml"]
      countIncrementalSlides: true
      ratio: "16:9"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina = 3, eval = FALSE)

xaringanExtra::use_xaringan_extra(c(
  "tile_view",  # type 'o' to see an overview of the slides
  "clipboard",  # copy-paste of the code chunks
  "panelset",   # panels, https://pkg.garrickadenbuie.com/xaringanExtra/panelset/
  "freezeframe" # so gifs play when we get to the slide
  ))
```

class: title-slide, inverse, bottom
background-image: url(`r params$png_background`)
background-size: cover

# `r rmarkdown::metadata$title`
### `r paste0("CFE R Training - Module ", params$module)`

<br/>

`r rmarkdown::metadata$author` and `r rmarkdown::metadata$ta`

---
class: middle

# Useful links

[Slides](`r params$url_slides`), if you want to navigate on your own

[RStudio Project](`r params$url_project`), to try out the exercises

[Teams Space](`r params$url_teams`), for discussions

[Github repository](`r params$url_github`), for later reference


---
# A regular slide

With text. Let's see the text.

```{r}
1 + 1
2 + 2 #<<
```


---
class: inverse, middle, left
background-image: url(`r params$png_background`)
background-size: cover

# Thank you!
## Any questions?

